### 2015-01-11 paper/Content/01introduction.tex
Aktuelle Gartner Zahl
lower case app

\IEEEPARstart{T}{he \emph{Android}} operating system is one of the most 
commonly used in mobile industry. After its first presentation in 2007, the open source system started its successful journey and became the leading mobile operating system in 2010 \cite{PassiveMVC}. According to Gartner \cite{GartnerAndroid2014}, there will be 1.1 billion \emph{Android}-based devices sold in 2014.

@@

To answer these questions, a prototypical App is built using the MVP approach.

In the next section we shortly show what core components, provided by the \emph{Android} SDK, need to be considered for our MVP implementation. In addition, we elaborate what types of \emph{Model-View-Presenter} approaches exist and which one we have chosen to build our App prototype. This is followed by an detailed explanation how we applied MVP to the Android SDK and how we built our App prototype. The last section concludes our findings.

>>>>

\IEEEPARstart{T}{he \emph{Android}} operating system is one of the most 
commonly used in mobile industry. After its first presentation in 2007, the open source system started its successful journey and became the leading mobile operating system in 2010 \cite{PassiveMVC}. According to Gartner \cite{GartnerAndroid2015}, there will be over 1.4 billion \emph{Android}-based devices sold in 2015.

@@

To answer these questions, a prototypical app is built using the MVP approach.

In the next section we shortly show what core components, provided by the \emph{Android} SDK, need to be considered for our MVP implementation. In addition, we elaborate what types of \emph{Model-View-Presenter} approaches exist and which one we have chosen to build our app prototype. This is followed by an detailed explanation how we applied MVP to the Android SDK and how we built our app prototype. The last section concludes our findings.
